---
title: "rq3"
author: "Clara Holst"
date: "`r Sys.Date()`"
output: html_document
---

Read all files from here: D:\UNI\4th Semester\Social and Cultural Dynamics\Misinformation\Data\

Research question here: Day: "D:\UNI\4th Semester\Social and Cultural Dynamics\Misinformation\Data\RQ3\Day" & Week: "D:\UNI\4th Semester\Social and Cultural Dynamics\Misinformation\Data\RQ3\Week"

Filenames:
RQ3_<sus><doubt><α><timepoint>

sus-doubt: Ratio of susceptible to doubter agents

α: Influence strength (1, 5, 10)

a = day-level measurements

b = week-level measurements
(e.g., 1a = day 1; 10b = week 10)

Variables:
Day,Time,Susceptible,Exposed,Believer,Doubter,Recovered,Disinformant,Total_Misinformed

```{r}

library(tidyverse)
library(stringr)

summarize_file <- function(file_path, time_type) {
  df <- read_csv(file_path, show_col_types = FALSE)
  fname <- basename(file_path)
  
  # Match filenames like RQ3_1_9_1a.csv
  parts <- str_match(fname, "RQ3_(\\d+)_(\\d+)_(\\d+)([ab])")
  if (any(is.na(parts))) {
    warning(paste("Skipping file due to filename mismatch:", fname))
    return(NULL)
  }
  
  sus <- as.integer(parts[2])
  doubt <- as.integer(parts[3])
  alpha <- as.integer(parts[4])
  label <- parts[5]
  
  # Get last day's value
  last_day <- max(df$Day, na.rm = TRUE)
  last_df <- df %>% filter(Day == last_day)
  
  # Convert to consistent time measure (day for a, week*7 for b)
  time_day <- ifelse(label == "a", last_day, last_day * 7)
  
  last_df %>%
    summarise(
      Mean_Believer = mean(Believer, na.rm = TRUE)
    ) %>%
    mutate(
      Time = time_day,
      Alpha = alpha,
      Sus = sus,
      Doubt = doubt,
      Ratio = paste0(sus, "-", doubt),
      TimeType = time_type,
      Filename = fname
    )
}

day_files <- list.files("D:/UNI/4th Semester/Social and Cultural Dynamics/Misinformation/Data/RQ3/Day", full.names = TRUE)
week_files <- list.files("D:/UNI/4th Semester/Social and Cultural Dynamics/Misinformation/Data/RQ3/Week", full.names = TRUE)

# Map and combine
all_summaries <- bind_rows(
  map(day_files, ~ summarize_file(.x, "Day")),
  map(week_files, ~ summarize_file(.x, "Week"))
)

```

```{r}
library(ggplot2)

# Plot: Believers over Time grouped by alpha
p <- ggplot(all_summaries, aes(x = Time, y = Mean_Believer, color = factor(Alpha))) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(
    title = "Misinformation Retention Over Time",
    subtitle = "Believer % across Susceptible-Doubter Ratios and Influence Levels",
    x = "Time (Days)",
    y = "Mean Number of Believers",
    color = "Influence (α)"
  ) +
  theme_minimal(base_size = 14)

# Save to PNG
ggsave("RQ3_Believers_Over_Time.png", plot = p, width = 10, height = 6, dpi = 300)

```

```{r}
library(ggplot2)
library(dplyr)

library(ggplot2)
library(dplyr)
library(tidyr)
ggplot(all_summaries, aes(x = factor(Alpha), y = Mean_Believer, group = Ratio, color = Ratio)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  facet_wrap(~ TimeType) +
  labs(
    title = "Mean % Believers over Influence Strength by Ratio",
    x = "Influence Strength (α)",
    y = "Mean % Believers",
    color = "Susceptible:Doubter Ratio"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

# Example: pivot data longer to plot multiple agent types in one plot
all_summaries_long <- all_summaries %>%
  mutate(Ratio = paste(Sus, Doubt, sep = ":")) %>%
  select(TimeType, Ratio, Alpha, Mean_Believer, Mean_Recovered, Mean_Exposed) %>%
  pivot_longer(cols = starts_with("Mean_"), 
               names_to = "AgentType", 
               values_to = "MeanPercent") %>%
  mutate(
    AgentType = case_when(
      AgentType == "Mean_Believer" ~ "Believer",
      AgentType == "Mean_Recovered" ~ "Recovered",
      AgentType == "Mean_Exposed" ~ "Exposed",
      TRUE ~ AgentType
    ),
    Alpha = factor(Alpha)  # for discrete x-axis
  )

ggplot(all_summaries_long, aes(x = Alpha, y = MeanPercent, group = AgentType, color = AgentType)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  facet_grid(TimeType ~ Ratio) +
  labs(
    title = "Misinformation Retention Over Influence Strength and Agent Ratios",
    subtitle = "Day vs Week measurements, by Susceptible:Doubter ratios",
    x = "Influence Strength (α)",
    y = "Mean % of Agents",
    color = "Agent Type"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text = element_text(face = "bold"),
    legend.position = "bottom"
  )

# Check what mean columns exist
names(all_summaries)


```
```{r}
library(tidyverse)

# Assuming 'all_summaries' dataframe has columns:
# TimeType, Ratio, Alpha, Mean_Believer, Mean_Recovered, Mean_Exposed

# Basic check which mean columns exist
mean_cols <- c("Mean_Believer", "Mean_Recovered", "Mean_Exposed")
mean_cols <- mean_cols[mean_cols %in% colnames(all_summaries)]

# Pivot longer to plot all agents in one plot with color by agent
plot_data <- all_summaries %>%
  select(TimeType, Ratio, Alpha, all_of(mean_cols)) %>%
  pivot_longer(
    cols = all_of(mean_cols),
    names_to = "Agent",
    values_to = "Mean"
  )

# Create plot
p <- ggplot(plot_data, aes(x = factor(Alpha), y = Mean, group = interaction(Ratio, Agent), color = Agent)) +
  geom_line(aes(linetype = Ratio), size = 1.1) +
  geom_point(aes(shape = Ratio), size = 3) +
  facet_wrap(~ TimeType) +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Mean % Agents over Influence Strength (α) by Susceptible:Doubter Ratio",
    subtitle = "Faceted by TimeType (Day vs Week)",
    x = "Influence Strength (α)",
    y = "Mean Percentage",
    color = "Agent Type",
    linetype = "Ratio (Sus:Doubt)",
    shape = "Ratio (Sus:Doubt)"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.margin=margin()
  )

# Save plot to PNG
ggsave("RQ3_Misinformation_Plot.png", p, width = 12, height = 7, dpi = 300)

# Print plot in RStudio viewer
print(p)

```
```{r}
library(tidyverse)

# Check mean columns present
mean_cols <- c("Mean_Believer", "Mean_Recovered", "Mean_Exposed")
mean_cols <- mean_cols[mean_cols %in% colnames(all_summaries)]

# Prepare data in long format
plot_data <- all_summaries %>%
  select(TimeType, Ratio, Alpha, all_of(mean_cols)) %>%
  pivot_longer(
    cols = all_of(mean_cols),
    names_to = "Agent",
    values_to = "Mean"
  )

# Plot with Ratio as color, Agent as linetype and shape
p <- ggplot(plot_data, aes(x = factor(Alpha), y = Mean, group = interaction(Ratio, Agent), color = Ratio)) +
  geom_line(aes(linetype = Agent), size = 1.1) +
  geom_point(aes(shape = Agent), size = 3) +
  facet_wrap(~ TimeType) +
  scale_color_brewer(palette = "Dark2") +  # Distinct colors for ratios
  labs(
    title = "Mean % Agents over Influence Strength (α) by Susceptible:Doubter Ratio",
    subtitle = "Faceted by TimeType (Day vs Week)",
    x = "Influence Strength (α)",
    y = "Mean Percentage",
    color = "Ratio (Sus:Doubt)",
    linetype = "Agent Type",
    shape = "Agent Type"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.margin=margin()
  )

# Save to PNG file
ggsave("RQ3_Misinformation_Plot_byRatioColor.png", p, width = 12, height = 7, dpi = 300)

# Display plot
print(p)

```

```{r}
library(tidyverse)

# Prepare long format data
mean_cols <- c("Mean_Believer", "Mean_Recovered", "Mean_Exposed")
mean_cols <- mean_cols[mean_cols %in% colnames(all_summaries)]

plot_data <- all_summaries %>%
  select(TimeType, Ratio, Alpha, all_of(mean_cols)) %>%
  pivot_longer(
    cols = all_of(mean_cols),
    names_to = "Agent",
    values_to = "Mean"
  ) %>%
  mutate(Alpha = factor(Alpha))

# Boxplot version:
p_box <- ggplot(plot_data, aes(x = Ratio, y = Mean, fill = Agent)) +
  geom_boxplot(alpha = 0.7, outlier.size = 1) +
  facet_grid(TimeType ~ Alpha, scales = "free_x", space = "free") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Distribution of Mean Agent Percentages by Ratio and Influence Strength",
    subtitle = "Faceted by TimeType (Day vs Week) and Influence Strength (α)",
    x = "Susceptible:Doubter Ratio",
    y = "Mean Percentage",
    fill = "Agent Type"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    strip.text = element_text(face = "bold")
  )

# Save to file
ggsave("RQ3_Boxplot_Misinformation.png", p_box, width = 14, height = 8, dpi = 300)

print(p_box)

```

```{r}

p_violin <- ggplot(plot_data, aes(x = Ratio, y = Mean, fill = Agent)) +
  geom_violin(alpha = 0.5, trim = FALSE) +
  geom_boxplot(width = 0.1, position = position_dodge(width = 0.9), outlier.size = 0.5) +
  facet_grid(TimeType ~ Alpha, scales = "free_x", space = "free") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Violin Plot of Agent Percentages by Ratio and Influence Strength",
    subtitle = "Faceted by Day/Week and α",
    x = "Susceptible:Doubter Ratio",
    y = "Mean Percentage",
    fill = "Agent Type"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.text = element_text(face = "bold"))

ggsave("RQ3_Violin_Misinformation.png", p_violin, width = 14, height = 8, dpi = 300)
print(p_violin)


```

```{r}
summary_stats <- plot_data %>%
  group_by(TimeType, Ratio, Alpha, Agent) %>%
  summarise(
    mean_val = mean(Mean, na.rm = TRUE),
    sd_val = sd(Mean, na.rm = TRUE),
    .groups = "drop"
  )

p_point <- ggplot(summary_stats, aes(x = Ratio, y = mean_val, color = Agent, group = Agent)) +
  geom_point(position = position_dodge(width = 0.8), size = 3) +
  geom_errorbar(aes(ymin = mean_val - sd_val, ymax = mean_val + sd_val),
                width = 0.3, position = position_dodge(width = 0.8)) +
  facet_grid(TimeType ~ Alpha, scales = "free_x", space = "free") +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Mean Agent Percentages with SD Error Bars",
    subtitle = "Faceted by Day/Week and Influence Strength (α)",
    x = "Susceptible:Doubter Ratio",
    y = "Mean Percentage",
    color = "Agent Type"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        strip.text = element_text(face = "bold"))

ggsave("RQ3_PointError_Misinformation.png", p_point, width = 14, height = 8, dpi = 300)
print(p_point)

```

```{r}
summary_table <- plot_data %>%
  group_by(TimeType, Ratio, Alpha, Agent) %>%
  summarise(
    mean = mean(Mean, na.rm = TRUE),
    sd = sd(Mean, na.rm = TRUE),
    median = median(Mean, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  arrange(TimeType, Alpha, Ratio, Agent)

# View summary table
print(summary_table)

# Save as CSV
write.csv(summary_table, "RQ3_Summary_Stats.csv", row.names = FALSE)

```

```{r}
library(tidyverse)

mean_cols <- c("Mean_Believer", "Mean_Recovered", "Mean_Exposed")
mean_cols <- mean_cols[mean_cols %in% colnames(all_summaries)]

plot_data <- all_summaries %>%
  select(TimeType, Ratio, Alpha, all_of(mean_cols)) %>%
  pivot_longer(
    cols = all_of(mean_cols),
    names_to = "Agent",
    values_to = "Mean"
  ) %>%
  mutate(Alpha = factor(Alpha))

p_box <- ggplot(plot_data, aes(x = Ratio, y = Mean, fill = Agent)) +
  geom_boxplot(alpha = 0.7, outlier.size = 1) +
  facet_grid(TimeType ~ Alpha, scales = "free_x", space = "free") +
  scale_fill_manual(values = c(
    "Mean_Believer" = "#D73027",
    "Mean_Recovered" = "#FC8D59",
    "Mean_Exposed" = "#FEE08B"
  )) +
  labs(
    title = "Distribution of Mean Agent Percentages by Ratio and Influence Strength",
    subtitle = "Faceted by TimeType (Day vs Week) and Influence Strength (α)",
    x = "Susceptible:Doubter Ratio",
    y = "Mean Percentage",
    fill = "Agent Type"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    strip.text = element_text(face = "bold")
  )

ggsave("RQ3_Boxplot_Misinformation_Red.png", p_box, width = 14, height = 8, dpi = 300)
print(p_box)

```


 