---
title: "Soccult_ABM_exam"
author: "Reka Forgo"
date: "`r Sys.Date()`"
output: html_document
---
Variables:
Day,Time,Susceptible,Exposed,Believer,Doubter,Recovered,Disinformant,Total_Misinformed

Read all files from here: ~/SocCult/Data

Sanity checks in this folder: ~/SocCult/Data

0 research question here: ~/SocCult/Data/RQ0

1 research question here: ~/SocCult/Data/RQ1

2 research question here: ~/SocCult/Data/RQ2

3 research question here: Day: ~/SocCult/Data/RQ3

```{r}
# Libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(hms)
library(lubridate)
library(stringr)
library(purrr)


# Define your specific colors
state_colors <- c(
  "Susceptible"   = "#00FF00",
  "Exposed"       = "#FFFF00",
  "Believer"      = "#FF0000",
  "Doubter"       = "#0000FF",
  "Recovered"     = "#A9A9A9",
  "Disinformant"  = "#800080"
)

```


#RQ3 (RF)
Methods for RQ3
To test the differences in the misinformation spread influenced by distribution of population, simulations were run on different Susceptible-Doubter ratios (10%–90% to 90% - 10%) with fixed Disinformant counts (n = 1) and α levels (1, 5, 10). Metrics track Believers and Recovered counts over time, to reveal short-term adoption versus long-term retention dynamics.


```{r}
#load in files for RQ3
#files are stored in ~/SocCult/Data/RQ3, we need to read in all data files, and store them with a simulation ID, as in simulations.csv and Filename column.

# 1. List all RQ3 files
files <- list.files(
  path       = "~/SocCult/Data/RQ3/daily",
  pattern    = "^RQ3_\\d+_\\d+_\\d+[ad]_.*\\.csv$",
  full.names = TRUE
)

# 2. Read & tag with regex captures for ratio, valence, and runType
rq3_raw <- files %>%
  set_names() %>%
  map_dfr(read.csv, .id = "filepath") %>%
  mutate(
    fn = basename(filepath),
    caps = str_match(fn, "^RQ3_(\\d+_\\d+)_(\\d+)([ad])_.*\\.csv$"),
    pop_ratio = caps[,2],
    valence   = as.integer(caps[,3]),
    runType   = caps[,4]
  ) %>%
  select(-fn, -caps)

# 3. Convert columns to appropriate types
rq3_raw$Day <- as.numeric(rq3_raw$Day)
rq3_raw$Time <- parse_hm(rq3_raw$Time)
rq3_raw$Susceptible <- as.numeric(rq3_raw$Susceptible)
rq3_raw$Exposed <- as.numeric(rq3_raw$Exposed)
rq3_raw$Believer <- as.numeric(rq3_raw$Believer)
rq3_raw$Doubter <- as.numeric(rq3_raw$Doubter)
rq3_raw$Recovered <- as.numeric(rq3_raw$Recovered)
rq3_raw$Disinformant <- as.numeric(rq3_raw$Disinformant)
rq3_raw$Total_Misinformed <- as.numeric(rq3_raw$Total_Misinformed)

# 4. Long format
rq3_long <- rq3_raw %>%
  pivot_longer(
    cols      = Susceptible:Recovered,    # melt only these 6 columns
    names_to  = "Agent_Group",               # new column with the old names
    values_to = "Count"                      # new column with their values
  )

# 5. Show the first few rows
head(rq3_long)

rq3_long <- rq3_long %>%
  filter(Day!= 2)# remove lines where Day = 2)

```

```{r}
#prep for plotting., average agent type counts across population distribtuions by time
rq3_avg <- rq3_long %>%
  # no valence in grouping → collapse across it
  group_by(pop_ratio, runType, Agent_Group, Day, Time) %>%
  summarise(
    MeanCount = mean(Count, na.rm = TRUE),
    .groups   = "drop"
  )

library(scales) 

ggplot(rq3_avg, aes(
    x     = Time,
    y     = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  #geom_smooth(size=0.5) +
  geom_line(size=0.5) +
  scale_x_time(limits = c(as_hms("07:00:00"), as_hms("24:00:00")),
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")) +
  facet_wrap(~ pop_ratio) +
  scale_color_manual(values = state_colors) +
  labs(
    title = "RQ3: Agent Group Counts by Population Distribution",
    x     = "Time",
    y     = "Mean Count"
  ) +
  theme_minimal() +
  theme(legend.position="bottom")

```

```{r}
#Plot without avg -ing over emotional valences
# 1) Summarise *with* valence (not collapsing it)
rq3_avg_day <- rq3_long %>%
  group_by(pop_ratio, valence, Agent_Group, Time) %>%
  summarise(
    MeanCount = mean(Count, na.rm = TRUE),
    .groups   = "drop"
  ) %>%
  ungroup() %>%
  mutate(
    valence = factor(valence, levels = c(1,5,10),
                     labels = c("Low (1)","Mid (5)","High (10)"))
  )

# 2) Plot with facet_grid(valence ~ pop_ratio)
ggplot(rq3_avg_day, aes(x = Time, y = MeanCount,
                        colour = Agent_Group, group = Agent_Group)) +
  geom_line(size = 0.3) +
  #geom_smooth(size = 0.5, method = "gam", se = FALSE) +
  facet_grid(rows = vars(valence), cols = vars(pop_ratio),
             switch = "y", scales = "fixed") +
  scale_x_time(
    breaks = breaks_width("4 hours"),
    limits = c(as_hms("07:00:00"), as_hms("24:00:00")),
    labels = label_time("%H:%M")
  ) +
  scale_color_manual(values = state_colors) +
  labs(
    title = "RQ3: Daily Agent counts by Valence & Population Mix",
    x     = "Hour of Day",
    y     = "Mean Count"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.placement     = "outside",
    strip.text.y.left   = element_text(angle = 0),
    axis.text.x = element_text(angle = 65, hjust = 1),
    legend.position     = "bottom",
    panel.grid.minor    = element_blank()
  ) 
```




#Week, RQ3

```{r}
#same with weekly data
# 1. List all RQ3 files
files2 <- list.files(
  path       = "~/SocCult/Data/RQ3/weekly",
  pattern    = "^RQ3_\\d+_\\d+_\\d+[bd]_.*\\.csv$",
  full.names = TRUE
)

# 2. Read & tag with regex captures for ratio, valence, and runType
rq3_raw2 <- files2 %>%
  set_names() %>%
  map_dfr(read.csv, .id = "filepath") %>%
  mutate(
    fn = basename(filepath),
    # regex: group1=“pop1_pop2”, group2=valence, group3=‘a’ or ‘d’
    caps = str_match(fn, "^RQ3_(\\d+_\\d+)_(\\d+)([bd])_.*\\.csv$"),
    pop_ratio = caps[,2],
    valence   = as.integer(caps[,3]),
    runType   = caps[,4]
  ) %>%
  select(-fn, -caps)

# 3. Convert columns to appropriate types
rq3_raw2$Day <- as.numeric(rq3_raw2$Day)
rq3_raw2$Time <- parse_hm(rq3_raw2$Time)
rq3_raw2$Susceptible <- as.numeric(rq3_raw2$Susceptible)
rq3_raw2$Exposed <- as.numeric(rq3_raw2$Exposed)
rq3_raw2$Believer <- as.numeric(rq3_raw2$Believer)
rq3_raw2$Doubter <- as.numeric(rq3_raw2$Doubter)
rq3_raw2$Recovered <- as.numeric(rq3_raw2$Recovered)
rq3_raw2$Disinformant <- as.numeric(rq3_raw2$Disinformant)
rq3_raw2$Total_Misinformed <- as.numeric(rq3_raw2$Total_Misinformed)

# 4. Long format
rq3_long2 <- rq3_raw2 %>%
  pivot_longer(
    cols      = Susceptible:Recovered,    # melt only these 6 columns
    names_to  = "Agent_Group",               # new column with the old names
    values_to = "Count"                      # new column with their values
  )

# 5. Show the first few rows
head(rq3_long2)


library(lubridate)

# choose an arbitrary origin – here “Day 1 at midnight”
origin <- as_datetime("2025-01-01 00:00:00", tz = "UTC")

rq3_long2 <- rq3_long2 %>%
  mutate(
    DateTime = origin + days(Day - 1) + Time)

```

```{r}
#prep for plotting., average agent type counts across population distribtuions by time
rq3_avg2 <- rq3_long2 %>%
  # no valence in grouping → collapse across it
  group_by(pop_ratio, runType, Agent_Group, DateTime) %>%
  summarise(
    MeanCount = mean(Count, na.rm = TRUE),
    .groups   = "drop"
  )

#create a plot with 9 subplots, one for each population distribution group (pop_ratio), have counts on the y axis and time on the x axis, with different colors for each agent group (Susceptible, Exposed, Believer, Doubter, Recovered).

ggplot(rq3_avg2, aes(
    x     = DateTime,
    y     = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  #geom_smooth(size=0.5) +
  geom_line(size=0.5) +
  facet_wrap(~ pop_ratio) +
  scale_color_manual(values = state_colors) +
  labs(
    title = "RQ3: Agent Group Counts by Population Distribution",
    x     = "DateTime",
    y     = "Mean Count"
  ) +
  theme_minimal() +
  theme(legend.position="bottom")
```

```{r}

rq3_long2 <- rq3_long2 %>%
  filter(Day!= 8) # remove lines where Day = 8)

rq3_avg2 <- rq3_long2 %>%
  group_by(pop_ratio, valence, Agent_Group, DateTime) %>%  # keep valence
  summarise(
    MeanCount = mean(Count, na.rm = TRUE),
    .groups   = "drop"
  ) %>%
  ungroup() %>%
  mutate(
    valence = factor(valence, levels = c(1, 5, 10),
                     labels = c("Low (1)", "Mid (5)", "High (10)"))
  )

ggplot(rq3_avg2, aes(x = DateTime, y = MeanCount,
                    colour = Agent_Group, group = Agent_Group)) +
  geom_line(size = 0.3) +
  #geom_smooth(size = 0.5, method = "gam", se = FALSE) +
  facet_grid(rows = vars(valence), cols = vars(pop_ratio),
             scales = "fixed", switch = "y") +
  scale_color_manual(values = state_colors) +
  scale_x_datetime(
    date_breaks = "1 day",        # one tick per day
    labels = function(x) day(x)           # just the day number (1–31)
  ) +
  labs(
    title = "RQ3: Agent Counts over a week by Valence and Population Mix",
    x     = "Date",
    y     = "Population Counts Mean"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    legend.position = "bottom"
  )
```


```{r}
# --- DAILY per‐run means ---
daily_run_summary <- rq3_raw %>%
  # keep filepath as your run ID
  group_by(run_id = filepath, pop_ratio, valence) %>%
  summarise(
    Mean_Believer  = mean(Believer,  na.rm=TRUE),
    Mean_Exposed   = mean(Exposed,   na.rm=TRUE),
    Mean_Recovered = mean(Recovered, na.rm=TRUE),
    .groups="drop"
  ) %>%
  transmute(
    TimeType = "Day",
    Ratio    = pop_ratio,
    Alpha    = valence,
    Mean_Believer, Mean_Exposed, Mean_Recovered
  )

# --- WEEKLY per‐run means ---
weekly_run_summary <- rq3_raw2 %>%
  # if you dropped filepath earlier, re‐read or keep it in your pipeline
  group_by(run_id = filepath, pop_ratio, valence) %>%
  summarise(
    Mean_Believer  = mean(Believer,  na.rm=TRUE),
    Mean_Exposed   = mean(Exposed,   na.rm=TRUE),
    Mean_Recovered = mean(Recovered, na.rm=TRUE),
    .groups="drop"
  ) %>%
  transmute(
    TimeType = "Week",
    Ratio    = pop_ratio,
    Alpha    = valence,
    Mean_Believer, Mean_Exposed, Mean_Recovered
  )

all_summaries <- bind_rows(daily_run_summary, weekly_run_summary)

```


```{r}

# Load all RQ3 summary files


mean_cols <- c("Mean_Believer", "Mean_Recovered")
mean_cols <- mean_cols[mean_cols %in% colnames(all_summaries)]

plot_data <- all_summaries %>%
  select(TimeType, Ratio, Alpha, all_of(mean_cols)) %>%
  pivot_longer(
    cols = all_of(mean_cols),
    names_to = "Agent",
    values_to = "Mean"
  ) %>%
  mutate(Alpha = factor(Alpha))

p_box <- ggplot(plot_data, aes(x = Ratio, y = Mean, fill = Agent)) +
  geom_boxplot(alpha = 0.7, outlier.size = 0.1, size = 0.1) +
  facet_grid(TimeType ~ Alpha, scales = "free_x", space = "free") +
  scale_fill_manual(values = c(
    "Mean_Believer" = "#FF0000",
    "Mean_Recovered" = "#A9A9A9"
  )) +
  labs(
    title = "Distribution of Mean Agent Percentages by Ratio and Influence Strength",
    subtitle = "Faceted by TimeType (Day vs Week) and Influence Strength (α)",
    x = "Susceptible:Doubter Ratio",
    y = "Mean Percentage",
    fill = "Agent Type"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    strip.text = element_text(face = "bold")
  )

#ggsave("RQ3_Boxplot_Misinformation_Red.png", p_box, width = 14, height = 8, dpi = 300)
print(p_box)


```

```{r}
library(zoo)  # for rollapply

# Full R pipeline for RQ3: separate daily vs. weekly dynamics plots
# 1a. Compute mean across runs
rq3_mean_day <- rq3_raw %>%
  group_by(Disinformant, valence, Time) %>%
  summarise(
    Exposed  = mean(Exposed,  na.rm = TRUE),
    Believer = mean(Believer, na.rm = TRUE),
    .groups  = "drop"
  )

# 1b. Compute instantaneous speeds & smooth
rq3_rates_day <- rq3_mean_day %>%
  arrange(Disinformant, valence, Time) %>%
  group_by(Disinformant, valence) %>%
  mutate(
    dt_mins    = as.numeric(difftime(Time, lag(Time), units = "mins")),
    dE         = Exposed  - lag(Exposed),
    dB         = Believer - lag(Believer),
    speed_E2B  = -dE / dt_mins * 1440,
    speed_B2R  = -dB / dt_mins * 1440,
    smooth_E2B = rollapply(speed_E2B, 3, mean, partial = TRUE, align = "center"),
    smooth_B2R = rollapply(speed_B2R, 3, mean, partial = TRUE, align = "center")
  ) %>%
  filter(!is.na(dt_mins) & dt_mins > 0) %>%
  ungroup()

# 1c. Pivot for plotting
rq3_plot_day <- rq3_rates_day %>%
  select(Disinformant, valence, Time, smooth_E2B, smooth_B2R) %>%
  pivot_longer(
    cols      = c(smooth_E2B, smooth_B2R),
    names_to  = "Transition",
    values_to = "Speed"
  ) %>%
  mutate(
    Transition = recode(Transition,
      smooth_E2B = "E → B (infection)",
      smooth_B2R = "B → R (recovery)"
    )
  )

# 1d. Plot daily dynamics
p_day <- ggplot(rq3_plot_day,
                aes(x = Time, y = Speed,
                    colour = factor(valence), group = valence)) +
  geom_line(size = 0.4) +
  #geom_smooth(method = "gam", se = FALSE, size = 0.6) +
  scale_colour_manual(
    name   = expression(valence),
    values = c("1"="yellow","5"="green","10"="blue")
  ) +
  facet_grid(Transition ~ Disinformant, scales = "fixed") +
  #ylim(0, 30) +
  theme_minimal(base_size = 10) +
  theme(
    legend.position   = "bottom",
    strip.text.y.left = element_text(angle = 0),
    axis.text.x       = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    title = "RQ3 – Daily Dynamics",
    x     = "Simulation time",
    y     = "Speed"
  )

# -------------------------
# 2. WEEKLY SIMULATION PIPE
# -------------------------


rq3_raw2 <- rq3_raw2 %>%
  mutate(
    DateTime = origin + days(Day - 1) + Time)

# 2a. Compute mean across runs
rq3_mean_week <- rq3_raw2 %>%
  group_by(Disinformant, valence, DateTime) %>%
  summarise(
    Exposed  = mean(Exposed,  na.rm = TRUE),
    Believer = mean(Believer, na.rm = TRUE),
    .groups  = "drop"
  )
# 2b. compute speeds in days → agents/day
rq3_rates_week <- rq3_mean_week %>%
  arrange(Disinformant, valence, DateTime) %>%
  group_by(Disinformant, valence) %>%
  mutate(
    dt_days    = as.numeric(difftime(DateTime, lag(DateTime), units = "mins")),
    dE         = Exposed  - lag(Exposed),
    dB         = Believer - lag(Believer),
    speed_E2B  = -dE / dt_days,     # agents per day
    speed_B2R  = -dB / dt_days,
    smooth_E2B = rollapply(speed_E2B, 3, mean, partial = TRUE, align = "center"),
    smooth_B2R = rollapply(speed_B2R, 3, mean, partial = TRUE, align = "center")
  ) %>%
  filter(dt_days > 0) %>%
  ungroup()

# 2c. pivot + compute simple week‐index
rq3_plot_week <- rq3_rates_week %>%
  select(Disinformant, valence, DateTime, smooth_E2B, smooth_B2R) %>%
  pivot_longer(
    c(smooth_E2B, smooth_B2R),
    names_to  = "Transition",
    values_to = "Speed"
  ) %>%
  mutate(
    Transition = recode(Transition,
      smooth_E2B = "E → B (infection)",
      smooth_B2R = "B → R (recovery)"
    ))

# 2d. plot with a single continuous scale
p_week <- ggplot(rq3_plot_week,
                 aes(x = DateTime, y = Speed,
                     colour = factor(valence), group = valence)) +
  geom_line(size = 0.4) +
  #geom_smooth(method = "gam", se = FALSE, size = 0.4) +
  scale_colour_manual(
    name   = expression(valence),
    values = c("1"="orange","5"="green","10"="blue")
  ) +
  facet_grid(Transition ~ Disinformant, scales = "fixed") +
  scale_x_datetime(
    date_breaks = "2 day",        # one tick per day
    labels = function(x) day(x)           # just the day number (1–31)
  ) +
  #xlim(as_datetime("2025-01-01 07:07:00", tz = "UTC"),
   #    as_datetime("2025-01-07 24:00:00", tz = "UTC")) +
  #ylim(0, 30) +
  theme_minimal(base_size = 10) +
  theme(
    legend.position   = "bottom",
    strip.text.y.left = element_text(angle = 0),
    axis.text.x       = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    title = "RQ3 – Weekly Dynamics",
    y     = "Speed"
  )
# --------------------------
# 3. DISPLAY BOTH SIDE BY SIDE
# --------------------------
p_day 
p_week

```
```{r}
# -------------------------
# 1. DAILY DYNAMICS PIPELINE
# -------------------------

# 1a. Compute mean across runs, including pop_ratio
rq3_mean_day <- rq3_raw %>%
  group_by(Disinformant, valence, pop_ratio, Time) %>%
  summarise(
    Exposed  = mean(Exposed,  na.rm = TRUE),
    Believer = mean(Believer, na.rm = TRUE),
    .groups  = "drop"
  )

# 1b. Compute instantaneous speeds & smooth
rq3_rates_day <- rq3_mean_day %>%
  arrange(Disinformant, valence, pop_ratio, Time) %>%
  group_by(Disinformant, valence, pop_ratio) %>%
  mutate(
    dt_mins    = as.numeric(difftime(Time, lag(Time), units = "mins")),
    dE         = Exposed  - lag(Exposed),
    dB         = Believer - lag(Believer),
    speed_E2B  = - dE / dt_mins,      # convert per‐minute → per‐day
    speed_B2R  = - dB / dt_mins,
    smooth_E2B = rollapply(speed_E2B, 5, mean, partial = TRUE, align = "center"),
    smooth_B2R = rollapply(speed_B2R, 5, mean, partial = TRUE, align = "center")
  ) %>%
  filter(!is.na(dt_mins) & dt_mins > 0) %>%
  ungroup()

# 1c. Pivot to long form for ggplot
rq3_plot_day <- rq3_rates_day %>%
  select(Disinformant, valence, pop_ratio, Time, smooth_E2B, smooth_B2R) %>%
  pivot_longer(
    cols      = c(smooth_E2B, smooth_B2R),
    names_to  = "Transition",
    values_to = "Speed"
  ) %>%
  mutate(
    pop_ratio  = factor(pop_ratio),
    Transition = recode(Transition,
      smooth_E2B = "E → B (infection)",
      smooth_B2R = "B → R (recovery)"
    )
  )

# 1d. Plot daily dynamics with facets by Disinformant × pop_ratio
p_day <- ggplot(rq3_plot_day,
                aes(x = Time, y = Speed,
                    colour = factor(valence), group = valence)) +
  #geom_line(size = 0.3, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, size = 0.5) +
  scale_colour_manual(
    name   = expression(valence),
    values = c("1"="orange","5"="green","10"="blue")
  ) +
  facet_grid(
    Transition ~ pop_ratio,
    scales   = "fixed",
    labeller = label_both
  ) +
  theme_minimal(base_size = 8) +
  theme(
    legend.position   = "bottom",
    strip.text.y.left = element_text(angle = 0),
    axis.text.x       = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    title = "RQ3 – Daily Dynamics",
    x     = "Simulation time",
    y     = "Speed"
  )

# -------------------------
# 2. WEEKLY DYNAMICS PIPELINE
# -------------------------

# 2a. Compute DateTime from Day + Time, and mean across runs
rq3_mean_week <- rq3_raw2 %>%
  mutate(
    DateTime = origin + days(Day - 1) + Time
  ) %>%
  group_by(Disinformant, valence, pop_ratio, DateTime) %>%
  summarise(
    Exposed  = mean(Exposed,  na.rm = TRUE),
    Believer = mean(Believer, na.rm = TRUE),
    .groups  = "drop"
  )

# 2b. Compute speeds in agents/day & smooth
rq3_rates_week <- rq3_mean_week %>%
  arrange(Disinformant, valence, pop_ratio, DateTime) %>%
  group_by(Disinformant, valence, pop_ratio) %>%
  mutate(
    dt_days    = as.numeric(difftime(DateTime, lag(DateTime), units = "mins")),
    dE         = Exposed  - lag(Exposed),
    dB         = Believer - lag(Believer),
    speed_E2B  = - dE / dt_days,     # agents per day
    speed_B2R  = - dB / dt_days,
    smooth_E2B = rollapply(speed_E2B, 5, mean, partial = TRUE, align = "center"),
    smooth_B2R = rollapply(speed_B2R, 5, mean, partial = TRUE, align = "center")
  ) %>%
  filter(!is.na(dt_days) & dt_days > 0) %>%
  ungroup()

# 2c. Pivot to long form
rq3_plot_week <- rq3_rates_week %>%
  select(Disinformant, valence, pop_ratio, DateTime, smooth_E2B, smooth_B2R) %>%
  pivot_longer(
    cols      = c(smooth_E2B, smooth_B2R),
    names_to  = "Transition",
    values_to = "Speed"
  ) %>%
  mutate(
    pop_ratio  = factor(pop_ratio),
    Transition = recode(Transition,
      smooth_E2B = "E → B (infection)",
      smooth_B2R = "B → R (recovery)"
    )
  )

# 2d. Plot weekly dynamics with same facet structure
p_week <- ggplot(rq3_plot_week,
                 aes(x = DateTime, y = Speed,
                     colour = factor(valence), group = valence)) +
  #geom_line(size = 0.3, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, size = 0.5) +
  scale_colour_manual(
    name   = expression(valence),
    values = c("1"="orange","5"="green","10"="blue")
  ) +
  facet_grid(
    Transition ~ pop_ratio,
    scales   = "fixed",
    labeller = label_both
  ) +
  scale_x_datetime(
    date_breaks = "2 day",
    labels      = function(x) day(x)
  ) +
  theme_minimal(base_size = 8) +
  theme(
    legend.position   = "bottom",
    strip.text.y.left = element_text(angle = 0),
    axis.text.x       = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    title = "RQ3 – Weekly Dynamics",
    x     = "Date",
    y     = "Speed"
  )

p_day
p_week
```


