---
title: "Soccult_ABM_exam"
author: "Reka Forgo"
date: "`r Sys.Date()`"
output: html_document
---
Variables:
Day,Time,Susceptible,Exposed,Believer,Doubter,Recovered,Disinformant,Total_Misinformed

Read all files from here: ~/SocCult/Data

Sanity checks in this folder: ~/SocCult/Data

0 research question here: ~/SocCult/Data/RQ0

1 research question here: ~/SocCult/Data/RQ1

2 research question here: ~/SocCult/Data/RQ2

3 research question here: Day: ~/SocCult/Data/RQ3

```{r}
# Libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(hms)
library(scales)
library(lubridate)
library(zoo)
# Define your specific colors
state_colors <- c(
  "Susceptible"   = "#00FF00",
  "Exposed"       = "#FFFF00",
  "Believer"      = "#FF0000",
  "Doubter"       = "#0000FF",
  "Recovered"     = "#A9A9A9",
  "Disinformant"  = "#800080"
)

```

#RQ2 (RF)
Methods for RQ2

Simulations to measure at what α does misinformation influence doubters, simulations were run to test populations of 29 Doubters + 1 Disinformant and 28 Doubters + 2 Disinformants, with sweeping α from 1 to 10. The Believer fraction is measured at 24 hours to identify the minimum α where Believers exceed 10%.



```{r}
#load in files for RQ2
#files are stored in ~/SocCult/Data/RQ2, we need to read in all data files, and store them with a simulation ID, as in simulations.csv and Filename column.
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)

data_dir <- "~/SocCult/Data/RQ2_5"
files <- list.files(data_dir, "\\.csv$", full.names = TRUE)

file_info <- tibble(
  path  = files,
  fname = basename(path)
) %>%
  # regex: RQ2_alpha_Param2[_YYYYMMDD_HHMMSS].csv
  mutate(m = str_match(
    fname,
    "^RQ2_(\\d+)_(\\d+)(?:_(\\d{8})_(\\d{6}))?\\.csv$"
  )) %>%
  { 
    bad <- filter(., is.na(m[,1]))$fname
    if (length(bad)) stop(
      "Filename pattern error on:\n", paste(bad, collapse = "\n")
    ) else .
  } %>%
  transmute(
    path,
    alpha       = as.numeric(m[,2]),
    Param2      = as.integer(m[,3]),
    fileDate    = if_else(
                    !is.na(m[,4]),
                    as.character(as.Date(m[,4], format = "%Y%m%d")),
                    NA_character_
                  ),
    fileTime    = if_else(
                    !is.na(m[,5]),
                    format(strptime(m[,5], "%H%M%S"), "%H:%M:%S"),
                    NA_character_
                  )
  ) %>%
  arrange(path) %>%
  mutate(Replication = row_number())

# read and attach
df_all <- file_info %>%
  mutate(data = map(path, read.csv, stringsAsFactors = FALSE)) %>%
  select(-path) %>%
  unnest(data)

# df_all now has: alpha, Param2, fileDate, fileTime, Replication, plus original CSV columns.

#remove filedate and file time columns
df_all <- df_all %>% select(-fileDate, -fileTime, -Param2)

#unique values in alpha columns

#how many lines are there / disinformant count?


```

```{r}
# 4) Convert columns to appropriate types

df_all$Day <- as.numeric(df_all$Day)
#remove lines where Day = 2
df_all <- df_all %>% filter(Day != 2) #(60 lines)



# Or, if it’s a character "HH:MM":
df_all$Time <- parse_hm(df_all$Time)

#convert agent group  counts to numeric
df_all$Susceptible <- as.numeric(df_all$Susceptible)
df_all$Exposed <- as.numeric(df_all$Exposed)
df_all$Believer <- as.numeric(df_all$Believer)
df_all$Doubter <- as.numeric(df_all$Doubter)
df_all$Recovered <- as.numeric(df_all$Recovered)
df_all$Disinformant <- as.factor(df_all$Disinformant)
df_all$Total_Misinformed <- as.numeric(df_all$Total_Misinformed)

#long format
df_long <- df_all %>% 
  pivot_longer(
    cols      = Susceptible:Recovered,    # melt only these 6 columns
    names_to  = "Agent_Group",               # new column with the old names
    values_to = "Count"                      # new column with their values
  )

#show df_long
head(df_long)



```


```{r}
library(dplyr)
library(lubridate)

df_peaks_all <- df_long %>%
  # include every Agent_Group
  group_by(Disinformant, alpha, Agent_Group) %>%
  # pick the single time‐point with the maximum Count per subgroup
  slice_max(Count, with_ties = FALSE) %>%
  ungroup() %>%
  # compute time‐to‐peak as hours since start
  mutate(
    TimeToPeakH = (Day - 1) * 24 +
                  hour(Time) +
                  minute(Time) / 60
  ) %>%
  transmute(
    Disinformant,
    alpha,
    Agent_Group,
    PeakDay     = Day,
    PeakTime    = Time,
    PeakCount   = Count,
    TimeToPeakH
  ) %>%
  arrange(Disinformant, alpha, Agent_Group)

print(df_peaks_all)

#save peaks all csv
write.csv(df_peaks_all, file = "~/SocCult/Data/RQ2_peaks_all.csv", row.names = FALSE)

```

```{r}
# 1. Compute the mean count per α × Agent_Group × Time
df_plot1 <- df_long %>%
  filter(Disinformant == 1) %>%                # only Disinformant = 1
  group_by(alpha, Agent_Group, Time) %>%
  summarise(MeanCount = mean(Count, na.rm = TRUE), .groups = "drop")

# 2. Plot: one facet per α, time‐series of each agent group
ggplot(df_plot1, aes(
    x      = Time,
    y      = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  scale_color_manual(values = state_colors) +
  geom_line(size = 0.5) +
  facet_wrap(~ alpha, ncol = 5) +                     # 10 panels, 5 across
  scale_x_time(                                       # if Time is hms/Period
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")
  ) +
  labs(
    title = "Agent Group Trajectories Over Time by α",
    x     = "Time of Day",
    y     = "Mean Agent Count",
    colour = "Agent Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

# 1. Compute the mean count per α × Agent_Group × Time
df_plot2 <- df_long %>%
  filter(Disinformant == 2) %>%                # only Disinformant = 1
  group_by(alpha, Agent_Group, Time) %>%
  summarise(MeanCount = mean(Count, na.rm = TRUE), .groups = "drop")

# 2. Plot: one facet per α, time‐series of each agent group
ggplot(df_plot2, aes(
    x      = Time,
    y      = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  scale_color_manual(values = state_colors) +
  geom_line(size = 0.5) +
  facet_wrap(~ alpha, ncol = 5) +                     # 10 panels, 5 across
  scale_x_time(                                       # if Time is hms/Period
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")
  ) +
  labs(
    title = "Agent Group Trajectories Over Time by α",
    x     = "Time of Day",
    y     = "Mean Agent Count",
    colour = "Agent Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )
#for disinformant = 3

df_plot3 <- df_long %>%
  filter(Disinformant == 3) %>%                # only Disinformant = 1
  group_by(alpha, Agent_Group, Time) %>%
  summarise(MeanCount = mean(Count, na.rm = TRUE), .groups = "drop")
# 2. Plot: one facet per α, time‐series of each agent group
ggplot(df_plot3, aes(
    x      = Time,
    y      = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  scale_color_manual(values = state_colors) +
  geom_line(size = 0.5) +
  facet_wrap(~ alpha, ncol = 5) +                     # 10 panels, 5 across
  scale_x_time(                                       # if Time is hms/Period
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")
  ) +
  labs(
    title = "Agent Group Trajectories Over Time by α",
    x     = "Time of Day",
    y     = "Mean Agent Count",
    colour = "Agent Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

# for disinformant = 4
df_plot4 <- df_long %>%
  filter(Disinformant == 4) %>%                # only Disinformant = 4
  group_by(alpha, Agent_Group, Time) %>%
  summarise(MeanCount = mean(Count, na.rm = TRUE), .groups = "drop")

# 2. Plot: one facet per α, time‐series of each agent group
ggplot(df_plot4, aes(
    x      = Time,
    y      = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  scale_color_manual(values = state_colors) +
  geom_line(size = 0.5) +
  facet_wrap(~ alpha, ncol = 5) +                     # 10 panels, 5 across
  scale_x_time(                                       # if Time is hms/Period
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")
  ) +
  labs(
    title = "Agent Group Trajectories Over Time by α",
    x     = "Time of Day",
    y     = "Mean Agent Count",
    colour = "Agent Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

# for disinformant = 5
df_plot4 <- df_long %>%
  filter(Disinformant == 5) %>%    
  group_by(alpha, Agent_Group, Time) %>%
  summarise(MeanCount = mean(Count, na.rm = TRUE), .groups = "drop")

# 2. Plot: one facet per α, time‐series of each agent group
ggplot(df_plot4, aes(
    x      = Time,
    y      = MeanCount,
    colour = Agent_Group,
    group  = Agent_Group
  )) +
  scale_color_manual(values = state_colors) +
  geom_line(size = 0.5) +
  facet_wrap(~ alpha, ncol = 5) +                     # 10 panels, 5 across
  scale_x_time(                                       # if Time is hms/Period
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")
  ) +
  labs(
    title = "Agent Group Trajectories Over Time by α",
    x     = "Time of Day",
    y     = "Mean Agent Count",
    colour = "Agent Group"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )



```


```{r}
# 1. average across reps, keep both Disinformant regimes
df_avg <- df_long %>%
  filter(Agent_Group %in% c("Believer","Doubter")) %>%
  group_by(Disinformant, alpha, Agent_Group, Time) %>%
  summarise(MeanCount = mean(Count), .groups = "drop")

# 2. one plot: colour=α, linetype=Agent_Group, thin lines, facet by Disinformant
ggplot(df_avg, aes(
    x       = Time,
    y       = MeanCount,
    colour  = factor(alpha),
    linetype = Agent_Group,
    group    = interaction(alpha, Agent_Group)
  )) +
  geom_line(size = 0.5) +  
  geom_hline(
    yintercept = 3,
    linetype   = "dashed",
    colour     = "red",
    size       = 0.3) +
  scale_linetype_manual(
    values = c("Believer" = "solid", "Doubter" = "dashed")
  ) +
  scale_x_time(                                     
    breaks = breaks_width("4 hours"),
    labels = label_time("%H:%M")
  ) +
  facet_wrap(~ Disinformant, nrow = 1, labeller = label_both) +
  labs(
    title    = "Mean Believer vs. Doubter Trajectories by α",
    x        = "Time",
    y        = "Mean Count",
    colour   = expression(alpha),
    linetype = "Agent Group"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x  = element_text(angle = 45, hjust = 1))


```
```{r}
#now instead of believer plot total misinformed

# 1. Average the Total_Misinformed column over repetitions
df_mis <- df_long %>%
  group_by(Disinformant, alpha, Time) %>%
  summarise(
    MeanMisinformed = mean(Total_Misinformed),
    .groups = "drop"
  )

# 2. Plot one thin line per α, red dashed threshold at y=3, faceted by Disinformant
ggplot(df_mis, aes(
    x      = Time,
    y      = MeanMisinformed,
    colour = factor(alpha),
    group  = alpha
  )) +
  geom_hline(
    yintercept   = 3,
    linetype     = "dashed",
    colour       = "red",
    size         = 0.3) +
  geom_smooth (size=0.5, method="gam", se = FALSE) +
  #geom_line(size = 0.5) +
  facet_wrap(~ Disinformant, nrow = 1, labeller = label_both) +
  labs(
    title  = "Mean Total-Misinformed Over Time by α",
    x      = "Time",
    y      = "Mean Misinformed",
    colour = expression(alpha)
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x  = element_text(angle = 45, hjust = 1))

#export df_long to a csv

write.csv(df_long, file = "~/SocCult/RQ2_df_long.csv", row.names = FALSE)


```

```{r}

ggplot(df_mis, aes(
    x      = Time,
    y      = MeanMisinformed,
    colour = alpha,      # use numeric alpha here
    group  = factor(alpha)
  )) +
  geom_hline(
    yintercept   = 3,
    linetype     = "dashed",
    colour       = "red",
    size         = 0.3
  ) +
  #geom_line(size=0.5, alpha=0.6) +
  geom_smooth(size=0.5, method="gam", se = FALSE) +
  facet_wrap(~ Disinformant, nrow = 1, labeller = label_both) +
  # continuous colour gradient from α = 1 (light) to α = 10 (dark)
  scale_colour_gradient(
    low    = "yellow",
    high   = "darkblue",
    limits = c(1, 10),
    breaks = 1:10,
    name   = expression(alpha)
  ) +
  labs(
    title  = "Mean Total-Misinformed Over Time by α",
    x      = "Time",
    y      = "Mean Misinformed"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x  = element_text(angle = 45, hjust = 1))

```
```{r}


df_all2 <- df_all %>% rename(t = Time)

df_mean <- df_all2 %>%
  group_by(Disinformant, alpha, t) %>%
  summarise(
    Exposed  = mean(Exposed,  na.rm=TRUE),
    Believer = mean(Believer, na.rm=TRUE),
    .groups  = "drop"
  )

# 3. Compute diffs & empirical speeds within each (Disinformant, α)
df_rates <- df_mean %>%
  arrange(Disinformant, alpha, t) %>%
  group_by(Disinformant, alpha) %>%
  mutate(
    dt_mins    = as.numeric(difftime(t, lag(t), units="mins")),
    dE         = Exposed  - lag(Exposed),
    dB         = Believer - lag(Believer),
    speed_E2B  = -dE        / dt_mins,       # agents/day
    speed_B2R  = -dB        / dt_mins,
    smooth_E2B = rollapply(speed_E2B, 9, mean,
                           partial=TRUE, align="center"),
    smooth_B2R = rollapply(speed_B2R, 9, mean,
                           partial=TRUE, align="center")
  ) %>%
  filter(dt_mins > 0) %>%
  ungroup()

# 4. Pivot longer for ggplot
df_plot <- df_rates %>%
  select(Disinformant, alpha, t, smooth_E2B, smooth_B2R) %>%
  pivot_longer(
    cols      = c(smooth_E2B, smooth_B2R),
    names_to  = "Transition",
    values_to = "Speed"
  ) %>%
  mutate(
    Transition = recode(Transition,
      smooth_E2B = "E → B",
      smooth_B2R = "B → R"
    )
  )

#have the scales the same on both y axes

ggplot(df_plot, aes(x = t, y = Speed, colour = alpha)) +
  geom_line(na.rm = TRUE, alpha = 0.1, size = 0.5) +
  geom_smooth(aes(group = factor(alpha)), method = "loess", se = FALSE, size = 0.5) +
  scale_colour_gradient(
    low    = "yellow",
    high   = "darkblue",
    limits = c(1, 10),
    breaks = 1:10,
    name   = expression(alpha)
  ) +
  # separate rows for infection vs. recovery, columns for each Disinformant
  facet_grid(Transition ~ Disinformant, scales = "free_y") +
  labs(
    x      = "Time",
    y      = "Speed",
    colour = expression(alpha),
    title  = "Infection vs. Recovery Speeds by Disinformant count & α"
  )  +
  #scale_y_continuous(limits = c(-0.02, 0.02)) +
  ylim(-0.02, 0.02) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x     = element_text(angle = 45, hjust = 1)
  )


```

```{r}


# 1. Average the Total_Misinformed column over repetitions
df_mis <- df_all %>%
  group_by(Disinformant, alpha, Time) %>%
  summarise(
    MeanMisinformed = mean(Believer),
    .groups = "drop"
  )

# 2. Plot one thin line per α, red dashed threshold at y=3, faceted by Disinformant
ggplot(df_mis, aes(
    x      = Time,
    y      = MeanMisinformed,
    colour = factor(alpha),
    group  = alpha
  )) +
  geom_hline(
    yintercept   = 3,
    linetype     = "dashed",
    colour       = "red",
    size         = 0.3) +
  geom_smooth (size=0.5, method="gam", se = FALSE) +
  #geom_line(size = 0.5) +
  facet_wrap(~ Disinformant, nrow = 1, labeller = label_both) +
  labs(
    title  = "Mean Total-Misinformed Over Time by α",
    x      = "Time",
    y      = "Mean Misinformed",
    colour = expression(alpha)
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x  = element_text(angle = 45, hjust = 1))

#export df_long to a csv

#write.csv(df_long, file = "~/SocCult/RQ2_df_long.csv", row.names = FALSE)


```


